---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  word_document: default
---

```{r}
library(readr)
Universities <- read_csv("C:/Trading detail/STUDY/01_MSBA/02 MSBA ML/03/Universities.csv")
View(Universities)


library(tidyverse)
library(factoextra)
library(ISLR)
library(caret)

summary(Universities)

```


a.  Remove all records with missing measurements from the dataset.
```{r}
# remove na in r - remove rows - na.omit function / option

set.seed(123)
univ <- na.omit(Universities) 


univ<-univ[,c(-1,-2,-3)]
summary(univ)
```

b. For all the continuous measurements, run K-Means clustering. Make sure to normalize the measurements. How many clusters seem reasonable for describing these data? What was your optimal K?
```{r}
##Scaling the data frame (z-score) 
univ <- scale(univ)
univ<- as.data.frame(univ)

### toFind best value of k by for total within sum of square
fviz_nbclust(univ, kmeans, method = "wss")   ###by applying 2 method "Wss" The chart shows that the elbow point 3 provides the best value for k.

### toFind best value of k by average silhouette width

fviz_nbclust(univ, kmeans, method = "silhouette")  ### applying "silhouette" method we see that 3 is the ideal number of clusters. 

fitk <- kmeans(univ,centers = 3)

fitk$size ## shows no. of observation in each cluster

fitk  ## summary of each cluster 


```


c. Compare the summary statistics for each cluster and describe each cluster in this context (e.g., “Universities with high tuition, low acceptance rate...”).



```{r}
fitk$centers  ## means of each cluster
##from means of the cluster we can conclude following information about different cluster

# plot an empty scatter plot

plot(c(0), xaxt = 'n', ylab = "", type = "l",
     ylim = c(min(fitk$centers), max(fitk$centers)), xlim = c(0, 18))
# label x-axes
axis(1, at = c(1:17), labels = names(fitk$centers))
# plot centroids
for (i in c(1:3))
  lines(fitk$centers[i,], lty = i, lwd = 2, col = ifelse(i %in% c(1, 2, 3),
                                                        "blue"))
# name clusters
text(x = 0.5, y = fitk$centers[, 1], labels = paste("Cluster", c(1:3)))

```

CLUSTER 3 :
has received high no. of application received,
has received high no. of application accepted,
high % of student enrolling for admission,
high no. of student with fulltime undergrad,
high no. of student with parttime undergrad,
low tution fee for in state student ,
high charges for additionalfees ,
high cost of books compared to others,
high personal expense,
good ratio for student to faculty,

Cluster 2 

high no of new student from top 10%,
high no of new student from top 25%,
low no. of student enrolled in undergrad,
high tution fee for in state student ,
high tution fee for out state student,
high occupncy for rooms,
high useage of board,
low personal expense,
high % of faculty with PHD, 
bad ratio for student to faculty,
high graduation rate,


Cluster 1 

received low application,
accepted low application,
low % of student enrolling for admission,
low no of new student from top 10%,
low no of new student from top 25%,
low no. of student with fulltime undergrad,
low tution fee for out state student,
low occupncy for rooms,
low useage of board,
low charges for additionalfees, 
low cost of books compared to others,
low  % of faculty with PHD ,
low graduation rate,


```{r}
## ploting information about cluster on graph

fviz_cluster(fitk,data = univ)
```


d. Use the categorical measurements that were not used in the analysis (State and Private/Public) to characterize the different clusters. Is there any relationship between the clusters and the categorical information?


```{r}
## adding catagorical variable into a table format


  univ1 <- na.omit(Universities) ## using orignal dataset to omit NA values

qwe <- cbind(univ1$`College Name`,univ1$State,univ1$`Public (1)/ Private (2)`,fitk$cluster) ### combining coloumn with cluters information and finding which university fallin which cluster

qwe <- as.data.frame(qwe) ## converting into dataframe

qwe$V3 <- factor(qwe$V3,levels = c(1,2),labels = c("public","private"))  ### defining levels for private ans public

qwe$V4 <- factor(qwe$V4,levels = c(1,2,3),labels = c("below avegrage ","above Average", "  average")) ## name cluster as different catagory

library(ggplot2)

ggplot(qwe, aes(x=qwe$V2,y=qwe$V3, color= qwe$V4)) +
  geom_point() 


head(qwe)




```


```{r}
head(qwe[qwe$V4=="below avegrage ",]) ### this show that good mix of private and  public university 
```
```{r}
head(qwe[qwe$V4=="  average",])  ### this show that more no. of public university 
```

```{r}
head(qwe[qwe$V4=="above Average",])  ###  this show that more no. of private university 
```


e. What other external information can explain the contents of some or all of these clusters?

```{r}
fitk$withinss

fitk$tot.withinss

fitk$betweenss
```


`

f. Consider Tufts University, which is missing some information. Compute the Euclidean distance of this record from each of the clusters that you found above (using only the measurements that you have). Which cluster is it closest to? Impute the missing values for Tufts by taking the average of the cluster on those measurements. 

```{r}
univ1<- univ1[,-c(1:3)]

Km<-kmeans(univ1,centers = 3)

b1<-mean(Km$centers[1,]) # Mean of Cluster 1
b2<-mean(Km$centers[2,]) # Mean of cluster 2
b3<-mean(Km$centers[3,]) # Mean of cluster 3
a1<-Universities[Universities$`College Name`=="Tufts University",]

View(a1)
a2<-apply(a1[,-c(1:3,10)],1,mean) # Mean of record
dist(rbind(a2,b1)) # Euclideam distance betweewn  cluster 1 mean and Tufts university data
dist(rbind(a2,b2))
dist(rbind(a2,b3))
a1$`# PT undergrad`<-3255.4528 # From the above, Mean value which is near to cluster 1. Hence replacing the missing value with mean value
univ3 <- na.omit(Universities)
uniV2<-rbind(univ3,a1)
View(uniV2)
uni2_z<-scale(uniV2[,-c(1:3)])
uni2_cluster<-kmeans(uni2_z,3)
uni2<-cbind(uniV2,uni2_cluster$cluster)
uni2[472,] # From the model, this uniersity falls under Cluster 2("Above Average")



### 2 part

univ2 <- Universities[ Universities$`College Name`== "Tufts University",] ## selecting Tufts university from original dataset

view(a1)
a1$`# PT undergrad` <- mean(Universities$`# PT undergrad`,na.rm=TRUE) ## selecting means value from coloumn and applying it to NA value for PT undergrad

a3 <- rbind(univ1,a1[,-c(1:3)])  ### combining dataset
view(a3)

a3_scale <- scale(a3) ### applying normalization

fitk2 <- kmeans(a3_scale,3) ### apply kmeans to dataset


a3<-cbind( a3,fitk2$cluster) ## combining cluster information col to dataset to find which cluster does tufts fallunder

a3[472,]  ### this university falls in cluster 1
```

